---
title: "ED-Report 6 (Data summary and matching fr preventable AE)"
date: "15/8/2024"
output: html_document
code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r, warning=FALSE ,message=FALSE , echo=FALSE}
library(dplyr)
library(zoo)
library(ggplot2)
library(readr)
library(fuzzyjoin)
library(tidyr)
library (MatchIt) 
library(fastDummies)
library(stargazer)

selected <- read_csv("/Users/mina/Desktop/AE project/sub_select.csv", col_types = cols(X1 = col_skip()))


selected <- selected %>%
  rename(shift_date = shift_date.y)%>%
  rename(shift_block = shift_block.y)%>%
  rename(ageyrs = ageyrs.y)%>%
  rename(sex = sex.y)%>%
  rename(site = site.y)%>%
  rename(chronic_condition = chronic_condition.y)%>%
  rename(number_ed_md_involved = number_ed_md_involved.y)%>%
  rename(ctas = ctas.y)%>%
  rename(pt_disposition = pt_disposition.y)%>%
  rename(AEoutcome = AEoutcome.y)%>%
  rename(number_ae = number_ae.y)%>%
  rename(censushour = censushour.y)%>%
  rename(wtbshour = wtbshour.x)

# Assuming your data frame is named df and the column is named preventable
selected$preventable <- as.logical(selected$preventable)
selected$preventable <- ifelse(selected$preventable == 1, TRUE, FALSE)
sub_select <- selected %>% select ("record_id","shift_date", "shift_block", "ageyrs", "sex", "site", "los", 
                                   "chronic_condition","number_ed_md_involved","number_staff","ctas",
                                   "pt_disposition", "AEoutcome","number_ae","preventable","waiting_to_be_seen","censushour","wtbshour")
sub_select <- sub_select %>% mutate(yq = as.yearqtr(shift_date, format = "%Y-%m-%d"))

sub_select <- sub_select %>% group_by(site, shift_block, shift_date, ctas) %>% mutate(avg_los_shift=mean(los,na.rm = TRUE)) #Avg Los of each ctas level within each shift

sub_select$los_cat <- "LOW"
sub_select$los_cat[sub_select$los> mean(sub_select$los, na.rm=TRUE)] <- "TRUE"
sub_select$shift_los_cat <- "LOW"
sub_select$shift_los_cat[sub_select$avg_los_shift> median(sub_select$avg_los_shift, na.rm=TRUE)] <- "TRUE"


sub_select$number_ae[is.na(sub_select$number_ae)]<-0

sub_select$pt_disposition_new <- 0
sub_select$pt_disposition_new[sub_select$pt_disposition==0] <-1
sub_select$pt_disposition_new[sub_select$pt_disposition==1|sub_select$pt_disposition==4] <-2
sub_select$pt_disposition_new[sub_select$pt_disposition==2|sub_select$pt_disposition==3] <-3
```

### **1- DATA SUMMARY**:
In this section, we investigated the raw data to see any potential specific pattern in the data. First, we checked number of **Preventable AE** and its ratio in **each quarter**:

**================ Precentage of AEoutcome in each quarter ================**
``` {r, warning=FALSE ,message=FALSE, echo=FALSE }
out <- table(sub_select$yq, sub_select$preventable)  # shows number of AE outcome in each quarter and year
out <- cbind(out, Precentage = out[,2]/rowSums(out))
out
```

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}

out <- as.data.frame(out)
out <- out %>% mutate(n=out[,2]+out[,1])
out <-  out %>% mutate(se=1.96*sqrt(Precentage*(1-Precentage)/n))
x <- rownames(out)
ggplot(data=out, aes(x=x, y=Precentage, fill = x)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Precentage-se, ymax=Precentage+se), width=.2,
                position=position_dodge(.9))+ 
  theme(legend.position = "none")+
  xlab("Year/Quarter")+
  geom_text(aes(label=round(Precentage, digit=3)), vjust=-0.5 , hjust=1.2, color="black", position = position_dodge(0.9),size=3)


```

As it can be seen from the above table, the ratio of AE in each quarter is almost consistent. With the same appraoch we can find the ratio of **Preventable AE** in each **site**

**================ Precentage of AEoutcome in each site ================**
``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
out <- table (sub_select$site, sub_select$preventable) 
out <- cbind(out, Precentage = out[,2]/rowSums(out))
out
```

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
out <- as.data.frame(out)
out <- out %>% mutate(n=out[,2]+out[,1])
out <-  out %>% mutate(se=1.96*sqrt(Precentage*(1-Precentage)/n))
x <- rownames(out)
ggplot(data=out, aes(x=x, y=Precentage, fill = x)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Precentage-se, ymax=Precentage+se), width=.2,
                position=position_dodge(.9))+ 
  theme(legend.position = "none")+
  xlab("Site Number")+
  geom_text(aes(label=round(Precentage, digit=3)), vjust=-0.5,hjust=1.05, color="black", position = position_dodge(0.9),size=3)

```


#### **1-1- Feature 1: LOS (Length of Stay)**


``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
summary(sub_select$los)
```
 We must also remember that we have **48 NA** values for LOS feature. We probably need to remove these observations in future analysis as imputing these values may result in wrong number and will affect our analysis. To investigate this feature more, we can visualize average of LOS for each type AEoutcome as shown below:

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(los, preventable) %>% group_by(preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=preventable, y=Ave_los, fill=preventable)) + 
  geom_bar(stat="identity" , position=position_dodge()) +  
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+ 
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5, hjust=1.7, color="black", size=3) +
  labs(fill = "preventable AEoutcome (Adverse Event Outcome)")+
  ylab("Average LOS")
```

We can also plot average LOS for each site for each type of AEoutcome as shown below:


``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(site, los, preventable) %>% group_by(site, preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=site, y=Ave_los, fill=preventable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_x_continuous(breaks=c(0:8))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.3, hjust=1.1, color="black", position = position_dodge(0.9),size=2.2)+
  ylab("Average LOS")

```

#### **1-2- Feature 2: ageyrs**
With the same approach as we showed for LOS, we can investigate age parameter as well. 

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(ageyrs, preventable) %>% group_by(preventable) %>% 
  summarise(Ave_age=round(mean(ageyrs, na.rm=TRUE), digit=2),n=n(), sd=sd(ageyrs,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=preventable, y=Ave_age, fill=preventable)) + 
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_age-se, ymax=Ave_age+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=Ave_age), vjust=-0.5, hjust=2.1, color="black", size=3)+
  labs(fill = "preventable AEoutcome (Adverse Event Outcome)")+
  ylab("Average Age")

```


``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(site, ageyrs, preventable) %>% group_by(site, preventable) %>% 
  summarise(Ave_age=round(mean(ageyrs, na.rm=TRUE), digit=2),n=n(), sd=sd(ageyrs,na.rm=TRUE), se=1.96*sd/sqrt(n))
ggplot(data=g, aes(x=site, y=Ave_age, fill=preventable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_age-se, ymax=Ave_age+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  scale_x_continuous(breaks=c(0:8))+
  geom_text(aes(label=Ave_age), vjust=-0.5, hjust=1.1, color="black", position = position_dodge(0.9), size=2.2)+
  ylab("Average Age")

```


``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(ctas, ageyrs, preventable) %>% group_by(ctas, preventable) %>% 
  summarise(Ave_age=round(mean(ageyrs, na.rm=TRUE), digit=2),n=n(), sd=sd(ageyrs,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=ctas, y=Ave_age, fill=preventable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_age-se, ymax=Ave_age+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  scale_x_continuous(breaks=c(0:8))+
  geom_text(aes(label=Ave_age), vjust=-0.5, hjust=1.1, color="black", position = position_dodge(0.9), size=3)+
  ylab("Average Age")

```


#### **1-4- Feature 4: ctas**

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
g <- sub_select %>% select(ctas, los, preventable) %>% group_by(ctas, preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE),n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=ctas, y=Ave_los, fill=preventable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_x_continuous(breaks=c(0:8))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5, hjust=1.1, color="black", position = position_dodge(0.9),size=3)+
  ylab("Average LOS")


```

#### **1-5- Feature 5: shift_block**

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}

g <- sub_select %>% select(shift_block, los, preventable) %>% group_by(shift_block, preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE),n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=shift_block, y=Ave_los, fill=preventable)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_x_continuous(breaks=c(0:8))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5, hjust=1.5, color="black", position = position_dodge(0.9),size=3)+
  ylab("Average LOS")


```


### **2- Matching**

In order to investigate the effect of **LOS** feature on **preventable AE**, we can use matching algorithm to find similar cases with negative and positive AEoutcome, put these cases in two different groups and then investigate the relationship between LOS for matched groups. To do this, we selected features that are listed below:

* shift_block
* ageyrs
* site
* ctas 
* los

  In order to match cases from positive and negative preventable AE we will go through these steps:
  
 1- Creating two pools of data. One for positive and one for negative preventable AEoutcome
 **Please note that since "LOS" is the parameter of interest, there is no point to for keeping NA values, so we removed rows which contained NA in LOS column.**

 2- Preparing dataset to pass it to **"Fuzzyjoin"** function
 
 3- Using “Fuzzyjoin” for matching data:

In order to find matches between two dataframes, we are going to use “Fuzzymatch”. The procedure we decided to use for matching is explained below:

* **Exact** matching for site feature
* **Exact** matching for ctas feature
* **Exact** matching for shift_block feature
* ageyrs within the range of **-20% and +20%** is considered as match value

Below is the result of matching algorithm:

``` {r, warning=FALSE ,message=FALSE, echo=FALSE}
# separating TRUE AEoutcome
AE_positive <- subset(sub_select, sub_select$preventable=="TRUE")
#AE_positive has 8 NA value for "los" for now we remove those rows 
AE_positive <- AE_positive[which(!is.na(AE_positive$los)),]
# separating FALSE AEoutcome
AE_Negative <- subset(sub_select, sub_select$preventable=="FALSE")
# Selecting specific feature for matching (shift_block, ageyrs, site, ctas, los)
AE_positive_s <- AE_positive %>% select(record_id, shift_block, ageyrs, site, ctas, los, avg_los_shift,shift_los_cat, preventable)
# Renaming AE_negative columns and make it proper to pass to fuzzyjoin function
AE_Negative_s <- AE_Negative %>% select(record_id, shift_block, ageyrs, site, ctas, los, avg_los_shift,shift_los_cat, preventable)
AE_Negative_s <- AE_Negative_s %>% rename(record_id_n=record_id ,shift_block_n = shift_block, ageyrs_n=ageyrs, 
                                          site_n=site, ctas_n=ctas, los_n=los, avg_los_shift_n= avg_los_shift, 
                                          shift_los_cat_n=shift_los_cat, preventable_n=preventable)

AE_positive_s$ageyrs_start <- AE_positive$ageyrs* 0.8  # first adding a range for acceptable ageyrs
AE_positive_s$ageyrs_end <- AE_positive$ageyrs * 1.2   # first adding a range for acceptable ageyrs

result_match<- fuzzyjoin::fuzzy_left_join(
  AE_positive_s, AE_Negative_s,
  by = c("shift_block" = "shift_block_n",
         "site" = "site_n",
         "ctas" = "ctas_n",
         "ageyrs_start" = "ageyrs_n",
         "ageyrs_end" = "ageyrs_n"),
  match_fun = list(`==`, `==`,`==`, `<=`, `>=`))

result_match <- result_match[-c(1,14)]
result_match <-result_match[which(!is.na(result_match$los_n)),]

nm1 <- sub("(\\d+|_n)$", "", names(result_match)) # Changing wide table format to long table format
lst1 <-  lapply(split.default(result_match, nm1), unlist, use.names = FALSE)
result_match_long <- data.frame(lapply(lst1, `length<-`, max(lengths(lst1))))[unique(nm1)]

result_match_modified <-result_match[which(!is.na(result_match$Ave_los_n)),]
result_match_modified <- ungroup(result_match_modified)
result_match_long<-result_match_long[which(!is.na(result_match_long$los)),]


```


```{r, layout="l-body-outset" , warning=FALSE ,message=FALSE, echo=FALSE}

library(knitr)
kable(head(result_match,10))

```

In the above table, the first 12 columns are related to positive AEoutcome group and the next columns are found matches from negative AEoutcome group. **Note that for one observation from positive AEoutcome group, we can have more than 1 match from negative AEoutcome group**. Since for each observation we can have multiple matches, we took an average from "LOS" of matches. Now we can compare the average "LOS" for different groups (negative and positive AEoutcome).


``` {r, layout="l-body-outset" , warning=FALSE ,message=FALSE, echo=FALSE}

g <- result_match_long %>% select(los,preventable) %>% group_by(preventable) %>% summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=preventable, y=Ave_los, fill=preventable)) + 
  geom_bar(stat="identity" , position=position_dodge()) + 
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5,hjust=1.8, color="black", size=3) +
  labs(fill = "Preventable AEoutcome (Adverse Event Outcome)")+
  ylab("Average LOS")

```

We can also compare the average LOS for matched data for different ctas:

``` {r, layout="l-body-outset" , warning=FALSE ,message=FALSE, echo=FALSE}

g <- result_match_long %>% select(ctas, los, preventable) %>% group_by(ctas, preventable) %>% summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=ctas, y=Ave_los, fill=preventable)) + 
  geom_bar(stat="identity" , position=position_dodge()) +
   geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5,hjust=1.3, color="black", size=2.5 ,
            position = position_dodge(0.9),size=2.5) +
  labs(fill = "Preventable AEoutcome (Adverse Event Outcome)")+
  ylab("Average LOS")

```

As it is shown above, the average LOS for each ctas and for positive AEoutcome is longer than the average LOS for each ctas with negative AEoutcome. We can investigate the same concept for each shift block and compare the average LOS for different group. The result is presented below:

``` {r, layout="l-body-outset" , warning=FALSE ,message=FALSE, echo=FALSE}

g <- result_match_long %>% select(shift_block, los, preventable) %>% group_by(shift_block, preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=shift_block, y=Ave_los, fill=preventable)) + 
  geom_bar(stat="identity" , position=position_dodge()) +  
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5, hjust=1.3, color="black", size=2.5 ,
            position = position_dodge(0.9),size=2.5) +
  labs(fill = "Preventable AEoutcome (Adverse Event Outcome)")+
  ylab("Average LOS")

```

As it can be seen, we came up with the same conclusion and that is the average LOS for positive AEoutcome group is longer than negative AEoutcome group. We can also check this for each site. The result is presented below:

``` {r, layout="l-body-outset" , warning=FALSE ,message=FALSE, echo=FALSE}

g <- result_match_long %>% select(site, los, preventable) %>% group_by(site, preventable) %>% 
  summarise(Ave_los=mean(los, na.rm=TRUE), n=n(), sd=sd(los,na.rm=TRUE), se=1.96*sd/sqrt(n))

ggplot(data=g, aes(x=site, y=Ave_los, fill=preventable)) + 
  geom_bar(stat="identity" , position=position_dodge()) +  
  geom_errorbar(aes(ymin=Ave_los-se, ymax=Ave_los+se), width=.2,position=position_dodge(.9))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  scale_fill_manual(values=c("turquoise3", "orangered3"))+
  geom_text(aes(label=round(Ave_los, digit=1)), vjust=-0.5, hjust=1.1,color="black", size=2.2  ,
            position = position_dodge(1.1),size=2.2) +
  scale_x_continuous(breaks=c(0:8))+
  labs(fill = "Preventable AEoutcome")+
  ylab("Average LOS")

```

Same as before, we ended up with the same trend for variation of LOS. AS it's represented, the average LOS for patients with positive AEoutcome in all sites are longer than patients with negative AEoutcome.


